\papertitle

### 2012-10-12 manuscript.tex
more citations

Autonomous control of flapping winged MAVs is a complex undertaking because of
the non-linear flight dynamics as presented
in~\cite{humbert:dipteran2,cheng:tandrdamping}. Although the dynamics of
flapping-winged flight can be averaged with respect to the wingbeat period as
presented in~\cite{Schenato:flightcontrol,cheng:tandrdamping}, we develop a
linear, one-dimensional model to predict the behavior of the system, similar
to~\cite{Shigeoka:ornithopter}. In addition to the nonlinearities, the system
is underactuated due to size constraints. Many of the methods for controlling
these platforms make extensive use of GPS in outdoor environments [CITATIONS]
and expansive motion capture systems in indoor environments. While operating
indoors, using GPS to estimate the pose of the MAV is not possible, and motion
capture requires expensive and stationary modification of the environment. The
power and payload limits on MAVs make on-board sensing difficult, so
multi-agent cooperative control schemes are apt solutions.

@@

%----------------------------------------------------------------------------%
\subsection{Pose Estimation}
%TODO ryan
The ground station performs simple two-dimensional pose estimation on the H$^2$Bird using 
a particle filter-based motion tracking algorithm. This pose estimate is 
the feedback input to the cooperative visual servoing feedback loop (Sec. \ref{sec:visual_servoing_concept}).

We limit our pose estimation approach to monocular two-dimensional object 
tracking in pixel-space. This allows us to perform high-rate video tracking 
using the modest computational resources available on the ground station, 
and similarly millirobotic ground vehicles.

~\cite{thrun2005probabilistic}

%----------------------------------------------------------------------------%
\subsection{Visual Servoing}
\label{sec:visual_servoing_concept}
%TODO ryan

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/block_diagrams.pdf}
\caption{Overall block diagram of the cooperative control system.}
\label{fig:block_diagram}
\end{figure}

@@

We gathered the data for the experiment by integrating the output of 
H$^2$Bird's on-board gyroscope data. We then used MATLAB [FOOTNOTE] to fit a 
simple low-order model, $H(s) = \frac{0.94782}{1+0.61998s}$, of the turning 
behavior to the step response with the physical heading as the state and the 
heading set point as the input. This model serves as a simplification of 
both the turning dynamics of the ornithopter and the on-board PID-based 
attitude controller. We use this model in Section~\ref{sec:visual_servoing} 
to determine the backwards reachable region for navigating through narrow passages.
%TODO H(s) in a labeled equation
%TODO footnote for MATLAB

@@

\begin{figure*}[tb]
\begin{minipage}[b]{0.45\linewidth}
\includegraphics[width=\textwidth]{figures/feasible_set.pdf}
\caption{Plot of backwards reachable set for successful window traversal.}
\label{fig:feasible_set}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\linewidth}
\centering
\centering
\includegraphics[width=\textwidth]{figures/heat_map.pdf}
\caption{Probability of success for all starting locations. This graphic is 
a result of a Monte Carlo simulation of the reachable set model, in which the 
initial heading of the H$^2$Bird is chosen uniformly at random from $(-90,90)$.}
\label{fig:heat_map}
\end{minipage}
\end{figure*}

>>>>

Autonomous control of flapping winged MAVs is a complex undertaking because of
the non-linear flight dynamics as presented
in~\cite{humbert:dipteran2,cheng:tandrdamping}. Although the dynamics of
flapping-winged flight can be averaged with respect to the wingbeat period as
presented in~\cite{Schenato:flightcontrol,cheng:tandrdamping}, we develop a
linear, one-dimensional model to predict the behavior of the system, similar
to~\cite{Shigeoka:ornithopter}. In addition to the nonlinearities, the system
is underactuated due to size constraints. Many of the methods for controlling
these platforms make extensive use of GPS in outdoor
environments~\cite{kingston:timeattitude, kanade:3dvision} and expansive
motion capture systems in indoor environments. While operating indoors, using
GPS to estimate the pose of the MAV is not possible, and motion capture
requires expensive and stationary modification of the environment. The power
and payload limits on MAVs make on-board sensing difficult, so multi-agent
cooperative control schemes are apt solutions.

@@

%----------------------------------------------------------------------------%
\subsection{Pose Estimation}
%TODO ryan

%----------------------------------------------------------------------------%
\subsection{Visual Servoing}
%TODO ryan

%TODO trim PDF
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/block_diagrams.pdf}
\caption{Overall block diagram of the cooperative control system.}
\label{fig:block_diagram}
\end{figure}

@@

We gathered the data for the experiment by integrating the output of
H$^2$Bird's on-board gyroscope data. We then used
MATLAB\footnote{\url{http://www.mathworks.com/products/matlab/}} to fit a
simple low-order model (Eq.~\ref{eq:transfer_func}) of the turning
behavior to the step response with the physical heading as the state and the
heading set point as the input. This model serves as a simplification of both
the turning dynamics of the ornithopter and the on-board PID-based attitude
controller. We use this model in Section~\ref{sec:visual_servoing} to
determine the backwards reachable region for navigating through narrow
passages.
\begin{equation}
\label{eq:transfer_func}
H(s) = \frac{0.94782}{1+0.61998s}
\end{equation}
%TODO H(s) in a labeled equation
%TODO footnote for MATLAB

@@

\begin{figure*}[tb]
\begin{minipage}[b]{0.45\linewidth}
\includegraphics[width=\textwidth]{figures/feasible_set.pdf}
\caption{Plot of backwards reachable set for successful window traversal.}
\label{fig:feasible_set}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\linewidth}
\centering
\centering
\includegraphics[width=\textwidth]{figures/heat_map.pdf}
\caption{CAPTION.}
\label{fig:heat_map}
\end{minipage}
\end{figure*}
